Categorical Predictor Embeddings in Actuarial Modeling

### 2021-03-25 manuscript/manuscript.Rmd
Update Transformer details in manuscript

Self-attention is the main building block of the current state of the art model for natural language processing, which is the Transformer model [@Vaswani2017]. The basic Transformer model applies a self-attention to the covariate matrix, $X'$ which is fed into the model, to produce a new matrix of covariates, $X^*$. These two matrices, the input matrix $X'$ and the output matrix $X^*$ are added (in an element-wise manner) together and then normalized. This matrix is then further processed through a neural network and subsequently, these processed covariates are used in the machine learning task.

The Transformer model is much more accurate on NLP tasks comapred to using the raw covariates before processing with a Transformer, to the extent that this model now underlies most NLP applications that use deep learning.

>>>>

Self-attention is the main building block of the current state of the art model for natural language processing, which is the Transformer model [@Vaswani2017]. A basic Transformer model applies self-attention to the covariate matrix, $X'$ which is fed into the model, to produce a new matrix of covariates, $X^*$. These two matrices, the input matrix $X'$ and the output matrix $X^*$ are added (in an element-wise manner) together and then normalized. This matrix is then further processed through a neural network and subsequently, these processed covariates are used in the machine learning task. Multiple Tranformer network "blocks" can be added to a network to create a deep Transformer network.

The Transformer model is much more accurate on NLP tasks compared to using the raw covariates before processing with a Transformer, to the extent that this model now underlies most NLP applications that use deep learning.
